---
title: "FD results"
author: "James Lawson"
date: "Monday, July 14, 2014"
output: html_document
---

Functional Diversity of riparian plant communities of south eastern Australia 
========================================================

This document presents the results of a functional diversity analysis using the following traits:

maxheight
SLA
seedmass
wood density
flowering period (proportion of year)
leaf length:width ratio
(leaf length)

Species by species trait correlations
--------------------------------------
Missing wood density cors due to missing values

```{r}
traits.naomit <- na.omit(traits)
cor(traits.naomit)
pairs(traits.naomit)

```


PCA of trait data 
--------------------------------------
```{r}
traits.PCA <- prcomp(traits.all, centre=TRUE, retx=TRUE)
summary(traits.PCA)
biplot(traits.PCA)
```


Trait correlations by CWM
--------------------------------------

```{r}
print(cor(CWM))
pairs(CWM)

```


FDis significant regressions
--------------------------------------
```{r}
getStats(hydroplots, hydroplots$FDis)

```

PCA over significant hydrological variables
-------------------------------------------
```{r}
FDis.signif <- data.frame(cbind(
#                                hydroplots["CVMDFWinter"],
#                                hydroplots["CVMDFAutumn"],
 #                               hydroplots["CVMDFSpring"],
#                                hydroplots["MDFMDFSummer"],
#                                hydroplots["MDFMDFSpring"],
                                hydroplots["M_MaxM"],
                                hydroplots["P_MaxM"],
                                hydroplots["M_MinM"],
                                hydroplots["M_MDFM"],
                                hydroplots["P_MDFM"],
                                hydroplots["AS20YrARI"],
                                hydroplots["CVAnnMRateFall"],
                                hydroplots["CVAnnMRateRise"],
                                hydroplots["LSPeak"],
                                hydroplots["CVAnnHSPeak"]
))

                                                    
FDis.signif.cor <- cor(FDis.signif)
print(FDis.signif.cor)

FDis.signif.PCA <- prcomp(FDis.signif, scale=TRUE, centre=TRUE, retx=TRUE)
summary(FDis.signif.PCA)
plot(FDis.signif.PCA)
biplot(FDis.signif.PCA)
```

