---
title: "FD results"
author: "James Lawson"
date: "Monday, July 14, 2014"
output: html_document
---

Functional Diversity of riparian plant communities of south eastern Australia 
========================================================

This document presents the results of a functional diversity analysis using the following traits:

- maxheight
- SLA
- seedmass
- wood density
- flowering period (proportion of year)
- leaf length:width ratio


**FDis and functional redundancy are significantly predicted by:**
- Flood magnitude (mean, extreme and CV)
- Low flow intensity
- Flood rise/fall rates
- Temporal uniformity of maximum, minimum and average flows (seasonal, interannual)
- Seasonality of flows


Relationships of hydrological variables with Functional Dispersion
------------------------------------------------------------------

```{r}

getStats(hydroplots, hydroplots$FDis, FD)

```

Relationships of hydrological variables with Functional Richness
------------------------------------------------------------------

```{r}

getStats(hydroplots, hydroplots$FRic, FD)

```

Relationships of hydrological variables with Functional Redundancy
------------------------------------------------------------------

```{r}

getStats(hydroplots, hydroplots$redun, FD)

```


Species by species trait correlations
--------------------------------------
Missing wood density cors due to missing values

```{r}
traits.naomit <- na.omit(traits)
cor(traits.naomit)
pairs(traits.naomit)

```


PCA of trait data 
--------------------------------------
```{r}
traits.PCA <- prcomp(traits.all, centre=TRUE, retx=TRUE)
summary(traits.PCA)
biplot(traits.PCA)
```


Trait correlations by CWM
--------------------------------------

```{r}
print(cor(CWM))
pairs(CWM)

```


PCA over significant hydrological variables
-------------------------------------------
```{r}
FDis.signif <- data.frame(cbind(
                                hydroplots["CVMDFWinter"],
                                hydroplots["CVMDFAutumn"],
                                hydroplots["CVMDFSummer"],
                                hydroplots["CVMDFSpring"],
                                hydroplots["MDFMDFAutumn"],
                                hydroplots["MDFMDFSummer"],
                                hydroplots["MDFMDFSpring"],
                                hydroplots["M_MaxM"],
                                hydroplots["P_MaxM"],
                                hydroplots["M_MinM"],
                                hydroplots["C_MinM"],
                                hydroplots["P_MinM"],
                                hydroplots["M_MDFM"],
                                hydroplots["C_MDFM"],
                                hydroplots["P_MDFM"],
                                hydroplots["AS20YrARI"],
                                hydroplots["CVAnnBFI"],
                                hydroplots["BFI"],
                                hydroplots["CVAnnMRateFall"],
                                hydroplots["CVAnnMRateRise"],
                                hydroplots["LSPeak"],
                                hydroplots["CVAnnHSPeak"],
                                hydroplots["HSPeak"]

                                
))

                                                    
FDis.signif.cor <- cor(FDis.signif)
print(FDis.signif.cor)

FDis.signif.PCA <- prcomp(FDis.signif, scale=TRUE, centre=TRUE, retx=TRUE)
summary(FDis.signif.PCA)
plot(FDis.signif.PCA)
biplot(FDis.signif.PCA)
```

