---
title: "FD results"
author: "James Lawson"
date: "Monday, July 14, 2014"
output: html_document
---

Functional Diversity of riparian plant communities of south eastern Australia 
========================================================

This document presents the results of a functional diversity analysis using the following traits:

maxheight
SLA
seedmass
wood density
flowering period (proportion of year)
leaf length:width ratio
(leaf length)

Species by species trait correlations
--------------------------------------
Missing wood density cors due to missing values

```{r}
traits.naomit <- na.omit(traits)
pairs(traits.naomit)
cor(traits.naomit)

```


PCA of trait data 
--------------------------------------
```{r}
traits.PCA <- prcomp(traits.all, centre=TRUE, retx=TRUE)
summary(traits.PCA)
biplot(traits.PCA)
```


Trait correlations by CWM
--------------------------------------

```{r}
pairs(CWM)
cor(CWM)

```


FDis significant regressions
--------------------------------------
```{r}
getStats(hydroplots, hydroplots$FDis)

```

PCA over significant hydrological variables
-------------------------------------------
```{r}
FDis.signif <- data.frame(cbind(
                          "CVMDFWinter" = hydro$CVMDFWinter,
                          "MDFMDFSummer" = hydro$MDFMDFSummer,
                          "MDFMDFSpring" = hydro$MDFMDFSpring,
                          "P_MaxM" = hydro$P_MaxM,
                          "CVAnnMRateRise"= hydro$CVAnnMRateRise,
                          "CVAnnHSPeak"= hydro$CVAnnHSPeak))
                                                    
FDis.signif.cor <- cor(FDis.signif)
View(FDis.signif.cor )
pairs(FDis.signif)

FDis.signif.PCA <- prcomp(FDis.signif, scale=TRUE, centre=TRUE, retx=TRUE)
summary(FDis.signif.PCA)
plot(FDis.signif.PCA)
biplot(FDis.signif.PCA)
```

